### 2019-06-20 2-Chapters/2-Chapter/chapter2.tex
Huge proof reading of Ch1 & Conclusion

One first need to observe that $R_T^{\cA} \geq 0$ for any $T$ and $\cA$, and that $R_T^{\cA} \leq \mu^* T$, so $R_T^{\cA} \leqT$ if the rewards lie in $[0,1]$.
Thus any algorithm has $R_T^{\cA} = \bigO{T}$, which justifies why we are interested in efficient algorithms that achieve at least a sub-linear regret, \ie, $R_T^{\cA} = \smallO{T}$.

@@

\begin{definition}\label{def:2:uniformlyEfficientAlgorithm}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
    An algorithm $\cA$ is \emph{uniformly efficient} if its (mean) regret satisfies
    $R_T^{\cA}(I) = \smallO_I{T^{\alpha}}$,
    for any value $\alpha>0$ and any problem instance $I\in \cI$.
    % where this notation means that the ``constant'' $C_{I,\alpha}$ can depend on the problem instance $I$ and on $\alpha$, but \emph{not} on the time horizon $T$.
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

>>>>

One first need to observe that $R_T^{\cA} \geq 0$ for any $T$ and $\cA$, and that $R_T^{\cA} \leq \mu^* T$, so $R_T^{\cA} \leq T$ if the rewards lie in $[0,1]$.
Thus any algorithm has $R_T^{\cA} = \bigO{T}$, which justifies why we are interested in efficient algorithms that achieve at least a sub-linear regret, \ie, $R_T^{\cA} = \smallO{T}$.

@@

\begin{definition}\label{def:2:uniformlyEfficientAlgorithm}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
    An algorithm $\cA$ is \emph{uniformly efficient} if its (mean) regret satisfies
    $R_T^{\cA}(I) = o_I(T^{\alpha})$,
    for any value $\alpha>0$ and any problem instance $I\in \cI$.
    % where this notation means that the ``constant'' $C_{I,\alpha}$ can depend on the problem instance $I$ and on $\alpha$, but \emph{not} on the time horizon $T$.
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

### 2019-06-20 2-Chapters/Conclusion/conclusion.tex
Huge proof reading of Ch1 & Conclusion

% \newpage
\abstractStartChapter{}%
%
This last chapter concludes the document, first by summarizing the previous chapters, and by giving a general conclusion of the thesis.
%
We highlight what we consider to be the most important directions of future works, as well as some promising directions that were shortly studied during my PhD but not discussed in the manuscript.

\minitocStartChapter{}

>>>>

% % \newpage
% \abstractStartChapter{}%
% %
% This last chapter concludes the document, first by summarizing the previous chapters, and by giving a general conclusion of the thesis.
% %
% We highlight what we consider to be the most important directions of future works, as well as some promising directions that were shortly studied during my PhD but not discussed in the manuscript.

% \minitocStartChapter{}
